Deep Probabilistic Models for Camera Geo-Calibration

### 2018-07-13 chapters/introduction/introduction.tex
first change

Before the father of computer asked this question, creating
machines that can think as human has been a dream through the human
history. In the late 18th century, Hungarian inventor, Wolfgan von
Kempelen, constructed an automatic machine called ``The Turk'' (also
known as the ``Mechanical Turk'') to play a chess game. Though it
proved to be an elaborate hoax, people's enthusiasm for machine
intelligence lasts till today. As one of the core elements of
intelligence, human vision plays an important role in our daily lives.
In order to make computer understand images, scholars had put a lot of
research efforts in the study of computer vision. In 1960s, MIT
professor Dr. Marvin Minsky asked his undergraduates to develop
programs that can recognize objects from a scene in their summer
project~\cite{boden2006mind}. Half a century has passed, the question
of this ``summer project'' still remains open.

The ultimate goal of image understanding is to transfer the visual
images into numerical or symbolic descriptions of the world
that are helpful for other thought processes for decision making.
In general, understanding images is not trivial for machines.
Under different scenarios, researchers divide image
understanding into different computer vision tasks. For example,
pedestrian detection is essential to autonomous driving, and image
retrieval to an image searching engine.

As one of the primary vision tasks, camera calibration plays an
important role in many applications like autonomous driving, indoor
layout estimation and image mensuration. 
In the camera pin-hole model, the projection from scene to the image
frame are determined by camera intrinsic and extrinsic parameters. 
The intrinsic parameters describe the information of camera
itself such as focal length, principal point \etc; 
The extrinsic parameters describe the external states of the
camera, such as the camera poses and translation under some
coordinate system.
Some applications like GIS and geo-localization are more interested in
calibrating the camera under geographic coordinates, namely knowing
the camera pose with respect to the ground reference frame (\ie ENU)
and camera location in geographic coordinates. We refer to such
calibration as \textbf{geo-calibration}.
The complete geo-calibration includes intrinsic (focal
length, principal points \etc) and extrinsic parameters.
In this work, our study mainly focuses on estimating geo-calibration
extrinsic parameters like camera pose and the
geo-orientation/geo-localization of the camera.

>>>>

Before the father of computer asked this question, creating
machines that can think as human has been a dream through the human
history. In 1960s, MIT professor Dr. Marvin Minsky asked his
undergraduates to develop programs that can recognize objects from a
scene in their summer project~\cite{boden2006mind}. Half a century has
passed, the question of this ``summer project'' still remains open.

The ultimate goal of image understanding is to transfer the visual
signals (images/videos) into abstract symbolic descriptions of the
world which are helpful for decision making.
In general, understanding images is not trivial for machines.
Under different scenarios, researchers divide image
understanding into different computer vision tasks. For example,
pedestrian detection is essential to autonomous driving, and image
retrieval to an image searching engine.

For many applications, knowing when, where, and in which direction a
picture was taken is important to understand the world. We refer to
this such a vision task as {\em geo-calibration}.
In current work of geo-calibration, most algorithms are
deterministic, which means they output fixed solutions. Deterministic
systems may seem straight-forward but they also have some 
drawbacks: 1) Deterministic systems can not handle uncertainties in
the real world very well. 2) they are not
friendly to applications developed with graphic models that are
interfaced with their outputs. To address these problems, We propose
to build probabilistic models for camera geo-calibration.

\section{Background}

As one of the primary vision tasks, camera calibration plays an
important role in many applications like autonomous driving, indoor
layout estimation and image mensuration. 
In the camera pin-hole model, the projection from scene to the image
frame are determined by camera intrinsic and extrinsic parameters. 
The intrinsic parameters describe the information of camera
itself such as focal length, principal point \etc; 
The extrinsic parameters describe the external states of the
camera, such as the camera poses and translation under some
coordinate system.

Some applications like GIS and geo-localization are more interested in
calibrating the camera under geographic coordinates, namely knowing
the camera pose with respect to the ground reference frame (\ie ENU)
and camera location in geographic coordinates. We refer to such
calibration as \textbf{geo-calibration}.
The complete geo-calibration includes intrinsic (focal
length, principal points \etc) and extrinsic parameters.
In this work, our study mainly focuses on estimating geo-calibration
extrinsic parameters like camera pose and the
geo-orientation/geo-localization of the camera.

### 2018-07-13 chapters/introduction/junk.tex
first change

>>>>

In the late 18th century, Hungarian inventor, Wolfgan von
Kempelen, constructed an automatic machine called ``The Turk'' (also
known as the ``Mechanical Turk'') to play a chess game. Though it
proved to be an elaborate hoax, people's enthusiasm for machine
intelligence lasts till today. As one of the core elements of
intelligence, human vision plays an important role in our daily lives.
In order to make computer understand images, scholars had put a lot of
research efforts in the study of computer vision.
